\documentclass{beamer}
\input{../common-definitions.tex}
\setbeamercovered{invisible}

\title{Copyright}
\date{October~$1^{\text{st}}$,~2013}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Quiz \hfill (Choose zero or more)}
Under the GNU manifesto, software companies could make money by:
\begin{enumerate}[(A)]
\item<1-2> distributing GNU software for a fee
\item<1-2> providing fee-based technical support
\item<1> charging when source code is copied
\item<1-2> making custom software for users
\end{enumerate}
\medskip
Stallman regrets writing
\begin{enumerate}[(A)]
\item<1-2> ``\ldots I am writing [GNU] so that I can give it away free to everyone\ldots''
\item<1-2> ``\ldots everyone will be able to obtain good system software free, just like air \ldots''
\item<1-2> ``Restricting copying is \ldots the most common basis [for business in software]\ldots''
\item<1-2> ``People who have studied the issue of intellectual property rights \ldots say that there is no intrinsic right\ldots''
\end{enumerate}
\end{frame}

\begin{frame}{Copyright}
Protection for original works of authorship:
\begin{itemize}
\item Literary, dramatic, musical, architectural, choreographic, etc.
\item \textbf{Not:} ideas, procedures, processes, principles, discoveries, slogans
\item Exclusive right to reproduce, distribute, perform/display
\item Lasts life of author + 70 years (in United States since 1978)
\end{itemize}
\bigskip
Berne Convention for the Protection of Literary and Artistic Works
\begin{itemize}
\item Created 9 September 1886 (United States joined in 1988)
\item International application of copyrights + minimum standards 
\item Copyright is automatic (may have reduced damages w/o notice)
\item Lasts at least 50 years
\item May allow ``fair use`` for criticism, comment, reporting, etc.
\end{itemize}
\end{frame}

\begin{frame}{GNU General Public License v3 \hfill\href{http://www.gnu.org/copyleft/gpl.html}{\beamergotobutton{GPL v3}}}
\begin{itemize}
\item[3.] Can I use GPL v3 libraries to implement Digital Rights Management (DRM) software? \\
\begin{itemize}
\item<2->Yes, but that software can then be legally cracked.
\end{itemize}
\item[4.] Can I sell someone else's GPL v3 code?
\begin{itemize}
\item<2->Yes.
\end{itemize}
\item[5.] Can I distribute GPL v3 source and a source with an incompatible license in the same zip file?
\begin{itemize}
\item<2->Yes, if they are fully independent.
\end{itemize}
\item[6.] Can I modify GPL v3 sources and charge people for this code?
\begin{itemize}
\item<2-> No, though you may charge shipping costs.
\end{itemize}
\item[6.] Can I implement hardware restrictions that keep people from modifying GPL v3 code?
\begin{itemize}
\item<2-> Yes, but only if they prevent \emph{everyone} from modifying the code.
\end{itemize}
\item[13.] Can I use GPL v3 libraries to implement a web service and not distribute the sources?
\begin{itemize}
\item<2-> Yes. To prevent this, use the GNU Affero General Public License.
\end{itemize}
\end{itemize}
\end{frame}

\end{document}
