\documentclass{beamer}
\input{../common-definitions.tex}

\title{Ethics of System Design}
\date{September~$12^{\text{th}}$,~2013}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Quiz}
Friedman \& Hahn would have a problem with\ldots \hfill (\emph{select zero or more})
\begin{enumerate}[(A)]
\item<1> Google's intelligent query auto-completion
\item<1-2> \href{http://www.nuance.com/landing-pages/products/nina/default.asp}{Nina Web}, Nuance's intelligent virtual assistant
\item<1-2> Siri, Apple's intelligent personal assistant
\item<1-2> WolframAlpha's ``\href{http://www.wolframalpha.com/}{Computational Knowledge Engine}''
% "mix cyan and magenta"
% "dow jones 2007 - 2009
% "integral of ln x"
\item<1> Xbox Kinect, which monitors and responds to how you move
\item<1-2> IMS Clinical, which provides clinical flowcharts for decision making
\item<1> Synergy's form filler, which pre-populates fields in clinical forms
\item<1> Coursera's automatic grading of programming assignments
\end{enumerate}
\end{frame}

\begin{frame}{High Frequency Trading}
Algorithmic trading at nanosecond speeds: \\
\href{http://www.colbertnation.com/the-colbert-report-videos/421265/november-14-2012/high-frequency-trading}{\beamergotobutton{Colbert Report: High Frequency Trading}} \\
\href{http://www.colbertnation.com/the-colbert-report-videos/421266/november-14-2012/high-frequency-trading---christopher-steiner}{\beamergotobutton{Colbert Report: High Frequency Trading -- Christopher Steiner}} \\
\bigskip
Is high frequency trading unethical according to Friedman \& Hahn?
\begin{itemize}
\item Does it protect the moral agency of humans?
\item Does it discourage a perception of moral agency in computers?
\end{itemize}
\bigskip
Does the Friedman \& Hahn ethical code sufficiently cover the issues?
\end{frame}

\begin{frame}{Deep Analytics}
IBM Watson: computer for playing Jeopardy \\
\href{http://www.youtube.com/watch?v=14r0eD2HWbo&t=14m51s}{\beamergotobutton{Jeopardy IBM Watson Episode 3}} \\
\href{http://www.youtube.com/watch?v=DywO4zksfXw}{\beamergotobutton{IBM Watson: The Science Behind an Answer}} \\
\bigskip
Is IBM Watson unethical according to Friedman \& Hahn?
\begin{itemize}
\item Does it protect the moral agency of humans?
\item Does it discourage a perception of moral agency in computers?
\end{itemize}
\bigskip
Does the Friedman \& Hahn ethical code sufficiently cover the issues?
\end{frame}

\end{document}
