% !TEX TS-program = pdflatexmk

\documentclass{beamer}
\input{../../common-definitions.tex}

\title{Test Driven Development}
\date{}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Quiz}
Which of the following did the study find? \hfill \textit{(Choose zero or more)}
\begin{enumerate}[(A)]
\item<1-2> Test-First programmers wrote more tests \visible<2->{\alert{(only at p=0.09!)}}
\item<1> Test-First programmers produced higher quality programs
\item<1> Test-First programmers were more productive
\item<1> Writing more tests improved quality
\item<1-2> Writing more tests increased productivity
\end{enumerate}
\medskip
What is the biggest weakness of the study? \hfill \textit{(Choose one)}
\begin{enumerate}[(A)]
\item<1> The programming language used (Java) is strongly typed
\item<1> The stories were artificially fine-grained
\item<1-2> Only one type of programming task was used
\item<1> The subjects were undergraduate computer science students
\end{enumerate}
\end{frame}

\begin{frame}{Testing Discussion}
\begin{itemize}[<+->]
\item Have you written tests for your code?
\item If you have, were they Test-First or Test-Last?
\item If you have, did they increase your productivity? Code quality?
\end{itemize}
\end{frame}

\begin{frame}{Test-First Development vs. Test-Driven Development}
Test-First Development:
\begin{enumerate}
\item\label{item:TFD:begin} Write a test and observe that it fails
\begin{itemize}
\item Where does the API come from?
\end{itemize}
\item Write code to make the test pass
\begin{itemize}
\item Code to meet requirements and for good design
\end{itemize}
\item Goto \ref{item:TFD:begin}
\end{enumerate}

\bigskip
\pause
Test-Driven Development
\begin{enumerate}
\item\label{item:TDD:begin} Write a test and observe that it fails
\begin{itemize}
\item API is developed via these tests!
\end{itemize}
\item Write the simplest code possible to make the test pass
\begin{itemize}
\item Focus is on meeting requirements
\end{itemize}
\item Refactor the code to improve the design
\begin{itemize}
\item Focus is on creating a good design
\end{itemize}
\item Goto \ref{item:TDD:begin}
\end{enumerate}
\end{frame}

\begin{frame}{Test-Driven Development}
\centering
\Huge TDD Demo
\end{frame}

\begin{frame}{Test-Driven Development Activity}
\setbeamercovered{invisible}
\centering
Pick some other aspect of PacMan and write a test

\pause
\bigskip
\noindent
Now compare with your teammates. Are the APIs compatible?
\end{frame}

\end{document}
