% !TEX TS-program = pdflatexmk

\documentclass{beamer}
\input{../../common-definitions.tex}

\title{Creating a Presentation}
\date{}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Quiz}
The best guest lecture presentation was by:
\begin{enumerate}[(A)]
\item Dr. Bangalore
\item Dr. Zhang
\item Mr. Warner
\item Dr. Pirkelbauer
\item Dr. Johnstone
\end{enumerate}
The worst guest lecture presentation was by:
\begin{enumerate}[(A)]
\item Dr. Bangalore
\item Dr. Zhang
\item Mr. Warner
\item Dr. Pirkelbauer
\item Dr. Johnstone
\end{enumerate}
\end{frame}

\begin{frame}{Presentation Rubric}
\begin{description}
\item[Content] Content is organized around key points, presentation flow shows the progression of the argument, and visuals are maximized while text is minimized.
\item[Oral Skills] Speech during the presentation is natural and fluent - not read or recited, and answers to questions demonstrate understanding of the topic.
\item[Use of Time] The presentation filled the 10 minutes allotted. Each 2 minutes shorter or longer than 10 minutes reduces the grade one category. (E.g., a 14 minute presentation is Marginal.)
\end{description}
\end{frame}

\begin{frame}{PowerPoint}
See: \href{http://www.feg-consulting.com/resource/practitioners-guide-to-hea/annexes-practitioners-guide/chapter-5/annex-d/}{Examples of Good and Bad Power Point Practice}\\
\bigskip
Pros:
\begin{itemize}
\item Easy editing: what you see is what you get
\item Standard: used in many companies, universities, institutes, etc.
\end{itemize}
Cons:
\begin{itemize}
\item Manual layout; aligning diagrams can be difficult
\item Poor support for rendering equations, etc.
\item May not display the same on all machines (but can export to PDF)
\end{itemize}
\end{frame}

\begin{frame}{\LaTeX\ and Beamer}
Demo\\
\bigskip
Pros:
\begin{itemize}
\item Automatic layout; aligning diagrams is easy
\item Excellent rendering of equations
\item Generates PDFs which display the same on all machines
\end{itemize}
Cons:
\begin{itemize}
\item Everything requires writing code
\item Visualizing result requires a compiler
\end{itemize}
\end{frame}

\begin{frame}{Prezi}
See: \href{http://prezi.com/c9pdlrpx3pr6/copy-of-presentation-on-presentations/}{Prezi Presentations}\\
\bigskip
Pros:
\begin{itemize}
\item Easy editing: what you see is what you get
\item Allows you to zoom in and out of details
\end{itemize}
Cons:
\begin{itemize}
\item Doesn't run on Linux
\item Poor support for rendering equations, etc.
\end{itemize}
\end{frame}

\end{document}
