% !TEX TS-program = pdflatexmk

\documentclass{beamer}
\input{../../common-definitions.tex}

\title{Ethics of System Design}
\date{}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Quiz}
Friedman \& Hahn would have a problem with\ldots \hfill (\emph{select zero or more})
\begin{enumerate}[(A)]
\item<1> Google's intelligent query auto-completion
\item<1-2> \href{http://www.wolframalpha.com/}{WolframAlpha}, a ``computational knowledge engine''
% "mix cyan and magenta"
% "dow jones 2007 - 2009
% "integral of ln x"
\item<1-2> \href{https://www.youtube.com/watch?v=8ciagGASro0}{Siri}, Apple's intelligent personal assistant
\item<1-2> \href{http://www.youtube.com/watch?v=5Y6DjWw_Td8}{Nina Web}, Nuance's intelligent virtual assistant
\item<1-2> IMS Clinical, which provides clinical flowcharts for decision making
\item<1> Synergy's form filler, which pre-populates fields in clinical forms
\item<1> Coursera's automatic grading of programming assignments
\item<1> Xbox Kinect, which monitors and responds to how you move
\end{enumerate}
\end{frame}

\begin{frame}{High Frequency Trading}
Algorithmic trading at nanosecond speeds: \\
\href{http://thecolbertreport.cc.com/videos/kvs6wn/high-frequency-trading}{\beamergotobutton{Colbert Report: High Frequency Trading}} \\
\href{http://thecolbertreport.cc.com/videos/ba8i6j/high-frequency-trading---christopher-steiner}{\beamergotobutton{Colbert Report: High Frequency Trading -- Christopher Steiner}} \\
\bigskip
Is high frequency trading unethical according to Friedman \& Hahn?
\begin{itemize}
\item Does it protect the moral agency of humans?
\item Does it discourage a perception of moral agency in computers?
\end{itemize}
Are there other ethical issues?
\end{frame}

\begin{frame}{Ethical High Frequency Trading}
How would you design an ethical high frequency trading system? \\
\bigskip
Describe:
\begin{itemize}
\item User interface
\item Implementation
\item Efficiency
\item Limitations
\end{itemize}
\end{frame}

\begin{frame}{Deep Analytics}
IBM Watson: computer for playing Jeopardy \\
\href{http://www.youtube.com/watch?v=tU6NcXqcRS4&t=5m37s}{\beamergotobutton{IBM Watson Jeopardy Day 3}} \\
\href{http://www.youtube.com/watch?v=DywO4zksfXw}{\beamergotobutton{IBM Watson: The Science Behind an Answer}} \\
\bigskip
Is IBM Watson unethical according to Friedman \& Hahn?
\begin{itemize}
\item Does it protect the moral agency of humans?
\item Does it discourage a perception of moral agency in computers?
\end{itemize}
Are there other ethical issues?
\end{frame}

\begin{frame}{Ethical Deep Analytics}
How would you design an ethical version of IBM Watson? \\
\bigskip
\bigskip
\pause
IBM Watson is currently being adapted to medical health records. \\
How does this change your design?
\end{frame}

\end{document}
